Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-14 manuscript/climate_sensitivity_draft.Rmd
minor changes
#105

- Individual-level drought resistance decreased with tree height and was not significantly linked to canopy position. The potentially greater rooting volume of larger trees did not confer an advantage in sites with low topgraphic wetness index. Resistance was greater among species whose leaves experienced less shrinkage upon desiccation and lost turgor (wilted) at more negative water potentials.

@@

We identified the three largest droughts within the time period 1950-2009, defining drought [@slette_how_2019] as events with both anomalously dry peak growing season climatic conditions. 
Specifically, we used the metric of Palmer Drought Severity Index (PDSI) during May-August (MJJA; Table S3), which were identified by @helcoski_growing_2019 as the months of the current year to which annual tree growth was most sensitive at this site. 
PDSI divisional data for Northern Virginia were obtained from NOAA (https://www7.ncdc.noaa.gov/CDO/CDODivisionalSelect.jsp) in December 2017. 
Based on this, we identified three drought years - 1966, 1977, and 1999 (Figs. **1**, **S2**, Table S3).

@@

Species traits... (Table 3, Fig. S#)

>>>>

- Individual-level drought resistance decreased with tree height, which was highly correlated with canopy position. The potentially greater rooting volume of larger trees did not confer an advantage in sites with low topographic wetness index. Resistance was greater among species whose leaves experienced less shrinkage upon desiccation and lost turgor (wilted) at more negative water potentials.

@@

We identified the three largest droughts within the time period 1950-2009, defining drought [@slette_how_2019] as events with anomalously dry peak growing season climatic conditions. 
Specifically, we used the metric of Palmer Drought Severity Index (PDSI) during May-August (MJJA; Table S3), which were identified by @helcoski_growing_2019 as the months of the current year to which annual tree growth was most sensitive at this site. 
PDSI divisional data for Northern Virginia were obtained from NOAA (https://www7.ncdc.noaa.gov/CDO/CDODivisionalSelect.jsp) in December 2017. 
Based on this, we identified three drought years - 1966, 1977, and 1999 (Figs. **1**, **S2**, Table S3).

@@

Species traits... (Table 3, Fig. **S4**)
